Radial and rotational velocities of young brown dwarfs and very low-mass stars in the Upper Scorpius OB association and the $\rho$~Ophiuchi cloud core

### 2006-04-10 BD_radvel/kurosawa.tex
committed by th
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@703 25464f21-6099-402c-b30a-640f1d40d38b

\usepackage{babel}
\makeatother
\begin{document}
\title[Radial and rotational velocities of young brown dwarfs candidates  in the Upper Sco and $\rho$~Oph]{Radial and rotational velocities of young brown dwarfs and very low-mass stars in Upper Scorpius OB association and $\rho$~Ophiuchi cloud core}

@@

We present the results of a radial velocity (RV) survey for 15 brown
dwarfs (BDs) and very low-mass (VLM) stars in the Upper Scorpius OB
association (UScoOB) and 3 BD candidates in the $\rho$~Ophiuchi
dark cloud core. We obtained high-resolution echelle spectra at VLT
using Ultraviolet and Visual Echelle Spectrograph (UVES) at two different
epochs for each object, and measured the shifts in their RVs to identify
candidates for binary/multiple systems in the sample. We found no
spectroscopic binary in our sample, based on the shape of cross-corelation
curves. We found 9 out of 18 (50 per cent) in our sample show a significant
RV change in 4--33~d time scale, and are considered as binary/multiple
`candidates.' The fraction slightly decreases to 43 per cent (6 out
of 14) if we consider the objects only in the UScoOB. These fractions
do not necessary represent that of a real binary population among
young BDs and VLM stars since their true multiplicities are still
to be confirmed by follow-up spectroscopic monitoring. Our RV-shift
tests successfully detected the recently confirmed 3 binaries in UScoOB
via high-resolution imaging technique. We found the RV dispersion
of the objects in UScoOB is very similar to that of the BDs and VLM
stars in Chamaeleon~I (Cha~I) previously studied by others. We also
measured the rotational velocities ($v\,\sin i$) of the samples,
and found good agreements with earlier studies. The distribution of
$v\,\sin i$ for the UScoOB objects peaks around $16.9\,\kmps$ which
is also similar to that of the Cha~I population.

@@

Most stars are member of binary systems; hence, it is important for
a star formation theory to be able to predict the binary fraction,
period distribution, and mass-ratio distribution of newly born stellar
objects across a wide range mass spectrum. The study of the individual
binary system is the only direct mean to determine the fundamental
stellar properties such as stellar masses and radii.

Recent high resolution imaging studies of young brown dwarfs (BDs)
and very low-mass (VLM) stars have placed strong constraints on binaries
with separations of $\sim1-100\,\mathrm{au}$. For example, Hubble
Space Telescope (\emph{HST}) observations of $\alpha$~Per and the
Pleiades indicates a binary fraction ($f$) of $>10$~per~cent with
a bias towards separations ($a$) of less than $15$~au, and a mass-ratio
($q$) of $>0.7$ \citep{martin:2003} for objects around and below
the hydrogen burning limit (see also \citealt{bouy:2006}). A similar
lack of wide binaries were found in the field T-dwarf study \citep{burgasser:2003},
while $f=15$~per~cent was determined by \citet{close:2003} using
the adaptive optics at Gemini North. They also found an upper limit
to the semi-major axis distribution of $\sim20\,\mathrm{au}$. An
\emph{HST} study of more than 80 field last M and L dwarfs \citep{gizis:2003}
indicated $f=15$~per~cent with separations in the range of 1.6--16~au.
For s small sample (12) of BDs and VLM stars (0.04--0.1~$\mathrm{M_{\odot}}$)
in Upper Scorpius OB association (UScoOB), \citet{kraus:2005} found
$f=25_{-8}^{+16}$~per~cent for $5\,\mathrm{au}<a<18\,\mathrm{au}$
by using similar imaging technique..

Using Monte Carlo simulation techniques, the data from radial velocity
surveys available on literatures, and carefully considering the sensitivity
and sampling biases, \citet{maxted:2005}  found an overall BD/VLM
binary frequency of 32--45 per~cent assuming $f=15$~per~cent for
$a>2.6$~au. A recent photometric study \citep{pinfield:2003} of
low-mass objects in Pleiades and Praesepe suggested, albeit indirectly,
$f$ as large as 50~per~cent. which would only be compatible with
direct imaging studies if 70--80~per~cent of those binaries have
$a<1\,\mathrm{au}$. For a more comprehensive review of the current
status of BD/VLM binary fraction and the separation distribution,
readers are refer to an excellent article on multiplicity studies
by \cite{burgasser:2006}.

The extensive imaging surveys provide excellent observational constraints
on wider BD+BD binaries, but it is now necessary to search for shorter
period BD+BD binaries systematically. Binaries with the separation
of less than 1~au are not resolved by current imaging technique,
but will be detectable as spectroscopic binaries, providing the mass-ratio
is not too extreme, and velocity separation is large enough. The first
BD+BD spectroscopic binary, PPl~15  \citep{basri:1999} showed a
double-peaked cross-correlation function with a maximum velocity separation
of $>70\,\kmps$. The binary was found to have an eccentric orbit
($e=0.4$) with a period of $\sim5.8\,\mathrm{d}$. \citet{basri:1999}
suggested that the formation process of substellar objects is biased
towards smaller separation binaries based on the short period of PPl~15
and the lack of Pleiades BD binaries with separations $>40\,\mathrm{au}$.
Note that the median separation of binaries with solar-type primaries
is 30~au \citet{duquennoy:1991}. The pioneer works on the RV studies
of BDs and VLMs are presented by \citet{guenther:2003}, \cite{kenyon:2005}
and \citet{joergens:2006} who found a sevral binary candidates among
them; however, the orbital parameters and masses of binaries remains
unknown because the follow-up spectroscopic monitoring is lacking
or still being taking places. In addition to the follow-up observations,
the number of BDs and VLM star binary candidates should be increased
to have a better statistics on the short period binary parameters.

The separation distribution of BD/VLM binaries is critical to understanding
their origin. There are two main models for the formation of BDs and
VLM stars. First, they formed in a similar manner to higher mass stars,
but from smaller-mass, denser molecular cloud core (e.g.~\citealt{padoan:2002}).
Second, BD/VLM objects have low masses because they are ejected from
the dense core in which they form via dynamical interactions in multiple
system, cutting off their accretion before they have reached stellar
masses (\citealt{reipurth:2001}; \citealt{bate:2002}). Alternatively,
there is a third model in which a free-floating BD or planetary-mass
object can be formed in the process of the photo-evaporation \citep{whitworth:2004}.
The outer layers of a pre-stellar core ($\sim0.2\,\mathrm{M_{\odot}}$)
removed by the strong radiation pressure from the nearby massive O
and B stars before the accretion onto the protostar at core centre
occurs. Apparently, this is more relevant to the high-mass star forming
clouds.

Due to the dynamical interaction involved in the second model, BD/VLM
binaries that survive are generally expected to have small separations.
In the first model, wider binaries may be expected to be more common.
\citet{bate:2002} suggested that close binaries ($a<10\,\mathrm{au}$)
do not form directly, but result from hardening of wider systems though
a combination of dynamical interactions, accretion and interactions
with circum-binary discs. If BD/VLM binaries have formed through such
mechanisms, one would expect to find binaries with 1--10~au separations
without also finding many with separation $<1$~au. If the absence/rarity
of binaries with 1~au were found, it would support the idea that
they are ejected quickly from multiple systems before they have undergone
the interactions that shorten the periods.

Our immediate aim is to identify spectroscopic and close BD/VLM binaries
using the high-resolution echelle spectroscopy at two epochs. This
experiment is sensitive to VLM binaries with separations of $<0.1$~au
which corresponds to a period of $\sim10\,\mathrm{d}$. A larger sample
of candidates will enable us to measure the binary fraction of these
short-period/close binaries (once confirmed), and address whether
there is a significant population of 'hidden' VLM companions. The
long term goal of this project to follow up the binary candidates
found in this paper by spectroscopically monitoring them in different
time scales, enabling us to obtain the radial velocity curves and
their minimum masses.

In Section~\ref{sec:observation-reduction}. we describe the observations
and the data reduction. The results of radial velocity and rotational
velocity ($v\,\sin i$) measurements are presented in Sections~\ref{sub:Radial-velocities}
and \ref{sub:Radial-velocities} respectively. We discuss the binary/multiplicity
fraction indicated by our RV survey in Section~\ref{sec:Binary-frequency}.
Finally, conclusions will be given in Section~\ref{sec:Conclusions}.

@@

Our sample consist of 18 young very low-mass objects previously identified
in the star forming regions: 15 objects in the Upper Scorpius OB association
($\mathrm{d\approx145\, pc}$, \citealt{dezeeuw:1999}) from the list
of \citet{ardila:2000} and 3 objects in the $\rho$~Ophiuchi cloud
core ($\mathrm{d\approx150\, pc}$, \citealt{dezeeuw:1997}) from
 \citet{luhman:1999}. The spectral type of the objects spreads between
M5 and M8.5, and the age $<\sim10\,\mathrm{Myr}$ (\citealt{luhman:1999};
\citealt{ardila:2000}; \citealt{muzerolle:2003}; \citealt{kraus:2005}).
The sample is not complete, and the selection is mainly based on the
brightness and the observability. The basic known properties of the
targets based on literatures is summarised in Table~\ref{tab:literatures}.

We obtained high resolution spectra with the Kueyen telescope of VLT
(Cerro Parnal, Chile) using the UVES echelle spectrograph. The observations
were carried out between April 5, 2004 and May 15, 2005 in the service
mode. For each object, the spectra were obtained at two different
epochs separated by 4--33~d to increase the chance of detectability
for multiplicities. For each object at a given night, two separate
spectra are obtained consecutively. This will allow us to derive more
reliable uncertainty estimates in the RV values of our targets (c.f.~\citealt{joergens:2006}).
The data was obtained using the red arm of UVES spectrograph with
two mosaic CCDs (EEV + MIT/LL with 2k$\times$4k pixels). The wavelength
coverage of 6708 -- 10,250~\AA\, and the spectral resolution $R\approx40,000$
were used. Unfortnately, the litheum lines at $\lambda\lambda6707.76$,$6707.93$
just fell shortward of the minimum wavelength. The slit width and
length of 1'' and 12'' are used respectively with a typical seeing
of 0.8''.

The data were reduced by the standard ESO pipeline procedures for
UVES echelle spectra. In summary, the data were corrected for bias,
interorder background, sky background, sky emission lines and cosmic
ray hits. Further, they were flattened, optimally extracted, and finally
the different orders were merged. No binning was performed to achieve
high resolution required for the RV measurements. The wavelength was
calibrated using the Thorium-Argon arc spectra with a typical value
of the standard deviation of the dispersion solution of 5~m\AA\,
which corresponds to 0.2~$\kmps$ at the central wavelength 8600~\AA.
However, the autoguiding of the telescope keeps the star at the centre
of the slit with about a tenth of the FWHM ($1\,\kmps$) which sets
the upper limit for the systematic error in the RV measurements \citep{bailer-jones:2004}.
The accuracy of the wavelength calibration will be demonstrated in
the RV measurements of a RV standard in the following section. A typical
signal-to-noise ratio (S/N) per wavelength bin of the spectra is about
15, and the heliocentric velocity correction was applied to the final
spectra.

@@

\caption{Summary of known properties of the targers from literatures: a.~\citet{luhman:1999} (original list for $\rho$~Oph), b.~\citet{ardila:2000} (original list for UScoOB),  c.~\citet{wilking:1999}, d.~\citet{muzerolle:2003}, e.~\citet{kraus:2005}, and f.~\citet{mohanty:2005}. }

@@

\caption{Summary of the observation, the heliocentric radial velocities ($\mathrm{RV}$) from two-epoch and the average rotational velocities ($v\sin i$). The uncetainties of relative radial velocties ($\sigma_{\mathrm{RRV}}$) with respect to the template star LHS~049 and the average radial velocties ($\overline{\mathrm{RV}}$) are also given. The last column indicates whether a target is a candidate for multiplicity i.e.~the measured radial velocity changes from two different epoch is larger than $1\,\sigma_{\mathrm{RRV}}$ of each others (c.f.~Fig.~\ref{fig:radvel01}).}

@@

\caption{Relative radial velocities (RVs) of objects measured in two different epochs. The vertical axes indicate  the amount of deviation ($\Delta \mathrm{RV}$) from the `average' radial velocitiy  ($\overline{\mathrm{RV}}$) in Table~\ref{tab:summary_results}), and the horizontal axes indicate the time of the observation in modified Julian date (MJD). The objects are considered to have a non-constant  RV when the error bars of two data points do not overlap each other. The non-constant RV objects are considered as binary/multiple candidates.}

@@

The radial velocities of each object are determined by using the cross-correlation
function of object spectra with that of a template star which has
a spectra type similar to those of our objects. By visual inspections,
the wavelength ranges used for the cross-correlation calculations
are chosen by avoiding the regions of spectra affected by the telluric
lines, the defects and the fringes (in near infrared) of CCDs, The
radial velocities of objects with respect to the template are obtained
by measuring the location of the peak in the cross-correlation function
which is fitted by the combination of two gaussian functions sharing
their centres and a constant term. LHS~49 (Proxima Cen, M5.5) is
chosen as the template for this purpose. The radial velocity of the
template object LHS~49 was obtained by measuring the wavelength shifts
of the prominent photospheric absorption features \ion{K}{i}~$\lambda\lambda$7664.911,~7698.974.
This gives us $\mathrm{RV_{LHS49}=}-22.6\pm0.5\,\kmps$, which is
in good agreement with the earlier measurement of \citet{garcia-sanchez:2001}
who found $\mathrm{RV_{LHS49}=}-21.7\pm1.8\,\kmps$. The heliocentric
RV of each object can be then calculated by adding $\mathrm{RV_{LHS49}}$
with the RV of each object with respect to LHS~49. In the following
measurements of the heliocentric radial velocities, our measurement
($\mathrm{RV_{LHS49}=}-22.6\pm0.5\,\kmps$) will be used for a consistency.

@@

The result of the heliocentric RV measurements (from two epochs for
each object) is summarised in Table~\ref{tab:summary_results} along
with the uncertainties. The table also lists the uncertainties in
the `relative' radial velocities ($\sigma_{\mathrm{RRV}}$) which
is the uncertainties of RVs with respect to the template star. The
two consecutive measurements of RVs (from same nights) are used to
find the RV of the night, and their uncertainties are obtained from
the standard deviations of the mean ($\sigma_{\mathrm{RRV}}$) and
the uncertainty of the template RV value (c.f.~\citealt{joergens:2006}).
The 'average' radial velocities ($\overline{\mathrm{RV}}$) of the
two epochs are also given in the same table for a reference. The $\overline{\mathrm{RV}}$
values of the objects in UScoOB are consistent with the earlier measurements
of \citet{muzerolle:2003} in Table~\ref{tab:literatures}, except
for the values for USco~66 and USco~75. This difference is not surprising
since the former is a known binary \citep{kraus:2005} and the latter
is a non-constant RV object (a candidate for a multiple) found in
the RV-shift test which will be discussed next.

For each object and for each RV measurement, the deviations ($\Delta\mathrm{RV}$)
from the average RV are computed and summaries in Fig.~\ref{fig:radvel01}
along with their uncertainties ($\sigma_{\mathrm{RRV}}$) in order
to aid the identifications of multiplicity candidates. Note that in
computing $\Delta\mathrm{RV}$ we do not require the knowledge of
absolute or the heliocentric radial velocities, but only the relative
velecities (with respect to a template). We choose a object as a candidate
when the 1$\sigma_{\mathrm{RRV}}$ error bar from each RV measurement
overlaps one another. Using this simple criteria, the candidate were
selected and indicated in the same table (Table~\ref{tab:summary_results}).
We found 9 out of 18 (50 per cent of) our sample are considered as
candidates. The recent observation of \citet{kraus:2005} (which was
not known to authors at the time of our observation: April--May, 2004)
confirms that USco~65 and USco~66 are multiple systems, and USco~109
is most likely a multiple system. In our RV-shift tests, we found
all the multiples confirmed by \citet{kraus:2005} in our multiple
candidates. Further they found USco~67, 128, 130, 132 as non-multiple,
and similarly we found them as 'non-candidates' for multiplicity.
The discrepancy between their results and ours are only in USco~75
and USco~112. While our results suggests that these are candidates
for multiple systems, \citet{kraus:2005} did not find them as multiple
systems. This difference may be caused by the difference in sensitivity
(on a binary separation) of the two different methods. Another possible
caused of the difference is that the uncertainties in RVs may be underestimated.
The surface activities of the objects may also contribute noise in
the RV measuements; however, the levels of th noise is expeted be
small for BD and VLM stars (c.f.~\citealt{joergens:2006}).

@@

According to the hydrodynamical calculation of a low-mass star forming
cluster of \cite{bate:2003} which yields a stellar density of $1.8\times10^{3}\,\mathrm{stars\, pc^{-3}}$,
the rms dispersion (1-D) of the stars and the BDs is $1.2\,\kmps$.
Similarly for the model with a higher stellar density ($2.6\times10^{3}\,\mathrm{stars\, pc^{-3}}$),
the rms dispersion is 2.5~$\kmps$ (\citealt{bate:2005}). The standard
deviation of $\overline{\mathrm{RV}}$ ($1.2\,\kmps$) found in our
analysis is more comparable the lower stellar density model.

@@

\caption{Histogram of the average heliocentric radial velocities (left) and the rotational velocities (right) of 14 UScoOB BD and VLM objects listed in Table~\ref{tab:summary_results} (excluding USco~121, non-member). The gaussian fit (dash) of the radial velociity distribution gives the standard deviation of  $1.2\,\kmps$ and the peak position of $-5.9\,\kmps$.  The log-normal fit (dash-dot) of  the rotational velocity distribution gives  the standard deviation $27.8\,\kmps$ and the peak poistion $16.9\,\kmps$.}

\label{fig:vrad_vrot_histrogram}

@@

The rotational velocities of the objects are determined by measuring
the widths of the cross correlation curves of the target spectra against
a templates spectra from an object which is known to have a very small
rotational velocity. The line broadening of the targets are assumed
to be dominated by rotational broadening. As in the cases for the
radial velocity measurements, LHS~49 is chosen for the template.
Using its known period ($P\approx83\,\mathrm{d}$, \citealt{benedict:1998})
and radius ($R_{*}\approx0.145\,\mathrm{R_{\odot}}$ from the VLTI
measurement by \citealt{segransan:2003}), the rotational velocity
of LHS~49 is estimated as $v\,\sin i=2\pi R_{*}/P\approx0.1\,\kmps$;
hence, negligibly small.

>>>>

\usepackage{babel}
\makeatother
\begin{document}
\title[Radial and rotational velocities of young BDs and VLM stars]{Radial and rotational velocities of young brown dwarfs and very low-mass stars in the Upper Scorpius OB association and the $\rho$~Ophiuchi cloud core}

@@

We present the results of a radial velocity (RV) survey of 15 brown
dwarfs (BDs) and very low-mass (VLM) stars in the Upper Scorpius OB
association (UScoOB) and 3 BD candidates in the $\rho$~Ophiuchi
dark cloud core. We obtained high-resolution echelle spectra at VLT
using Ultraviolet and Visual Echelle Spectrograph (UVES) at two different
epochs for each object, and measured the shifts in their RVs to identify
candidates for binary/multiple systems in the sample.
We found 9 out of 18 (50 per cent) in our sample show a significant
RV change in 4--33~d time scale, and are considered as binary/multiple
`candidates.' The fraction slightly decreases to 43 per cent (6 out
of 14) if we consider the objects only in the UScoOB. These fractions
do not necessary represent that of a real binary population among
young BDs and VLM stars since their true multiplicities are still
to be confirmed by follow-up spectroscopic monitoring. We found no
double-lined spectroscopic binaries in our sample, based on the shape of cross-corelation
curves. Our RV-shift tests successfully detected the recently confirmed 3 binaries in UScoOB
via high-resolution imaging technique. We found the RV dispersion
of the objects in UScoOB is very similar to that of the BDs and VLM
stars in Chamaeleon~I (Cha~I) previously studied by others. We also
measured the rotational velocities ($v\,\sin i$) of the sample,
and found good agreements with earlier studies. The distribution of
$v\,\sin i$ for the UScoOB objects peaks around $16.9\,\kmps$ which
is similar to that of the Cha~I population.

@@

Most stars are member of binary systems and it is therefore important that
a complete star formation theory be able to predict the binary fraction,
period distribution, and mass-ratio distribution of newly born stellar
objects across a wide range of masses. Furthermore, the study of the individual
binary system is the only direct means to determine the fundamental
stellar properties such as stellar masses and radii.

Recent high-resolution imaging studies of young brown dwarfs (BDs)
and very low-mass (VLM) stars have placed strong constraints on binaries
with separations of $\sim1-100\,\mathrm{au}$. For example, Hubble
Space Telescope (\emph{HST}) observations of $\alpha$~Per and the
Pleiades indicates a binary fraction ($f$) of $>10$~per~cent with
a bias towards separations ($a$) of less than $15$~au, and a mass-ratio
($q$) of $>0.7$ \citep{martin:2003} for objects around and below
the hydrogen burning limit (see also \citealt{bouy:2006}). A similar
lack of wide binaries was found in the field T-dwarf study \citep{burgasser:2003},
while $f=15$~per~cent was determined by \citet{close:2003} using
the adaptive optics at Gemini North. They also found an upper limit
to the semi-major axis distribution of $\sim20\,\mathrm{au}$. An
\emph{HST} study of more than 80 field last M and L dwarfs \citep{gizis:2003}
indicated $f=15$~per~cent with separations in the range of 1.6--16~au.
For s small sample (12) of BDs and VLM stars (0.04--0.1~$\mathrm{M_{\odot}}$)
in Upper Scorpius OB association (UScoOB), \citet{kraus:2005} found
$f=25_{-8}^{+16}$~per~cent for $5\,\mathrm{au}<a<18\,\mathrm{au}$
by using a similar imaging technique..

Using a Monte Carlo simulation, the data from radial velocity
surveys available in the literature, and by carefully considering the sensitivity
and sampling biases, \citet{maxted:2005}  found an overall BD/VLM
binary frequency of 32--45 per~cent assuming $f=15$~per~cent for
$a>2.6$~au. A recent photometric study \citep{pinfield:2003} of
low-mass objects in Pleiades and Praesepe suggested, albeit indirectly,
$f$ as large as 50~per~cent. which would only be compatible with
direct imaging studies if 70--80~per~cent of those binaries have
$a<1\,\mathrm{au}$. For a more comprehensive review of the current
status of BD/VLM binary fraction and the separation distribution,
readers are refer to a recent review of multiplicity studies
by \cite{burgasser:2006}.

The extensive imaging surveys provide excellent observational constraints
on wider BD+BD binaries, but it is now necessary to search for shorter
period BD+BD binaries systematically. Binaries with the separation
of less than 1~au are not resolved by current imaging techniques,
but will be detectable as spectroscopic binaries, providing the mass-ratio
is not too extreme, and velocity separation is large enough. The first
BD+BD spectroscopic binary, PPl~15  \citep{basri:1999} showed a
double-peaked cross-correlation function with a maximum velocity separation
of $>70\,\kmps$. The binary was found to have an eccentric orbit
($e=0.4$) with a period of $\sim5.8\,\mathrm{d}$. \citet{basri:1999}
suggested that the formation process of substellar objects is biased
towards smaller separation binaries based on the short period of PPl~15
and the lack of Pleiades BD binaries with separations $>40\,\mathrm{au}$.
Note that the median separation of binaries with solar-type primaries
is 30~au \citet{duquennoy:1991}. Pioneering work on the RVs
of BDs and VLMs are presented by \citet{guenther:2003}, \cite{kenyon:2005}
and \citet{joergens:2006} who found a several binary candidates;
however, the orbital parameters and masses of binaries remains
unknown because the follow-up spectroscopic monitoring is lacking
or still being undertaken. In addition to the follow-up observations,
the number of BDs and VLM star binary candidates needs to be increased
in order to have better statistics on short-period binary parameters.

The separation distribution of BD/VLM binaries is critical to understanding
their origin. There are two main models for the formation of BDs and
VLM stars: first, they formed in a similar manner to higher mass stars,
but from smaller-mass, denser molecular cloud core (e.g.~\citealt{padoan:2002});
second, BD/VLM objects have low masses because they are ejected from
the dense core in which they form via dynamical interactions in multiple
system, cutting off their accretion before they have reached stellar
masses (\citealt{reipurth:2001}; \citealt{bate:2002}). Alternatively,
there is a third model in which a free-floating BD or planetary-mass
object can be formed in the process of the photo-evaporation \citep{whitworth:2004} with
the outer layers of a pre-stellar core ($\sim0.2\,\mathrm{M_{\odot}}$)
removed by the strong radiation pressure from the nearby massive OB
 stars before the accretion onto the protostar at core centre
occurs.

Due to the dynamical interaction involved in the second model, BD/VLM
binaries that survive are generally expected to have small separations.
In the first model, wider binaries may be expected to be more common.
\citet{bate:2002} suggested that close binaries ($a<10\,\mathrm{au}$)
do not form directly, but result from hardening of wider systems though
a combination of dynamical interactions, accretion and interactions
with circum-binary discs. If BD/VLM binaries have formed through such
mechanisms, one would not expect to find binaries with 1--10~au separations
without also finding many with separation $<1$~au. If an absence/rarity
of binaries with 1~au were found, it would support the idea that
they are ejected quickly from multiple systems before they have undergone
the interactions that shorten their periods.

Our immediate aim is to identify spectroscopic and close BD/VLM binaries
using the high-resolution echelle spectroscopy at two epochs. This
experiment is sensitive to VLM binaries with separations of $<0.1$~au
which corresponds to a period of $\sim10\,\mathrm{d}$. A larger sample
of candidates will enable us to measure the binary fraction of these
short-period/close binaries (once confirmed), and address whether
there is a significant population of 'hidden' VLM companions. The
long term goal of this project to follow up the binary candidates
found in this paper by spectroscopically monitoring them over different
time scales, enabling us to obtain the radial velocity curves and
their minimum masses.

In Section~\ref{sec:observation-reduction}. we describe the observations
and the data reduction. The results of radial velocity and rotational
velocity ($v\,\sin i$) measurements are presented in Sections~\ref{sub:Radial-velocities}
and \ref{sub:Radial-velocities} respectively. We discuss the binary/multiplicity
fraction indicated by our RV survey in Section~\ref{sec:Binary-frequency}, and give
our conclusions in Section~\ref{sec:Conclusions}.

@@

Our sample consists of 18 young, very low-mass objects: 15 objects in the Upper Scorpius OB association ($\mathrm{d\approx145\, pc}$, \citealt{dezeeuw:1999}) from the list
of \citet{ardila:2000} and 3 objects in the $\rho$~Ophiuchi cloud
core ($\mathrm{d\approx150\, pc}$, \citealt{dezeeuw:1997}) from
 \citet{luhman:1999}. The spectral type of the objects range between
M5 and M8.5, and the age $<\sim10\,\mathrm{Myr}$ (\citealt{luhman:1999};
\citealt{ardila:2000}; \citealt{muzerolle:2003}; \citealt{kraus:2005}).
The sample is not complete, and the selection was solely based on 
brightness and the observability. The basic properties of the
targets based on the literature is summarised in Table~\ref{tab:literatures}.

We obtained high-resolution spectra with the Kueyen telescope of VLT
(Cerro Parnal, Chile) using the UVES echelle spectrograph. The observations
were carried out between 2004 April 5 and 2005 (XXX?)  May 15 in  service
mode. For each object, spectra were obtained at two different
epochs separated by several (between 4 and 33~d). For each object at a given 
night, two separate spectra are obtained consecutively. This allows us to derive more
reliable uncertainty estimates in the RV values of our targets (c.f.~\citealt{joergens:2006}).
The data were obtained using the red arm of UVES spectrograph with
two mosaic CCDs (EEV + MIT/LL with 2k$\times$4k pixels). The wavelength
coverage of 6708 -- 10,250~\AA\, and the spectral resolution $R\approx40,000$
were used. The slit width and length of 1'' and 12'' were used respectively with a typical seeing
of 0.8''.

The data were reduced via the standard ESO pipeline procedures for
UVES echelle spectra. In summary, the data were corrected for bias,
interorder background, sky background, sky emission lines and cosmic
ray hits. They were then flattened, optimally extracted, and finally
the different orders were merged. No binning was performed to achieve
high resolution required for the RV measurements. The wavelength was
calibrated using the Thorium-Argon arc spectra with a typical value
of the standard deviation of the dispersion solution of 5~m\AA\,
which corresponds to 0.2~$\kmps$ at the central wavelength 8600~\AA.
However, the autoguiding of the telescope keeps the star at the centre
of the slit with about a tenth of the FWHM ($1\,\kmps$) which sets
the upper limit for the systematic error in the RV measurements \citep{bailer-jones:2004}.
The accuracy of the wavelength calibration will be demonstrated in
the RV measurements of a RV standard in the following section. A typical
signal-to-noise ratio (S/N) per wavelength bin of the spectra is about
15, and the heliocentric velocity correction was applied to the final
spectra.

@@

\caption{Summary of known properties of the targets from literature: a.~\citet{luhman:1999} (original list for $\rho$~Oph), b.~\citet{ardila:2000} (original list for UScoOB),  c.~\citet{wilking:1999}, d.~\citet{muzerolle:2003}, e.~\citet{kraus:2005}, and f.~\citet{mohanty:2005}. }

@@

\caption{Summary of the observations, the heliocentric radial velocities ($\mathrm{RV}$) from two-epoch and the average rotational velocities ($v\sin i$). The uncetainties of relative radial velocties ($\sigma_{\mathrm{RRV}}$) with respect to the template star LHS~049 and the average radial velocties ($\overline{\mathrm{RV}}$) are also given. The last column indicates whether a target is a candidate for multiplicity i.e.~the measured radial velocity changes from two different epoch is larger than $1\,\sigma_{\mathrm{RRV}}$ of each others (c.f.~Fig.~\ref{fig:radvel01}).}

@@

\caption{Relative radial velocities (RVs) of objects measured in two different epochs. The vertical axes indicate  the amount of deviation ($\Delta \mathrm{RV}$) from the `average' radial velocitiy  ($\overline{\mathrm{RV}}$) in Table~\ref{tab:summary_results}), and the horizontal axes indicate the time of the observation in modified Julian date (MJD; XXX do you really mean MJD rather than heliocentric JD????). The objects are considered to have a non-constant  RV when the error bars of two data points do not overlap each other. The non-constant RV objects are considered as binary/multiple candidates.}

@@

The radial velocities of each object were determined by using the cross-correlation
function of the object spectrum with that of a template star which has
a spectra type. By visual inspection,
the wavelength ranges used for the cross-correlation calculations
are chosen by avoiding the regions of spectra affected by the telluric
lines, and defects and fringes (in near infrared) of the CCDs. The
radial velocities of objects with respect to the template are obtained
by measuring the location of the peak in the cross-correlation function
which is fitted by the combination of two gaussian functions sharing
their centres and a constant term (XXXX What does this mean?). LHS~49 (Proxima Cen, M5.5) was
chosen as the template for this purpose. The radial velocity of the
template object LHS~49 was obtained by measuring the wavelength shifts
of the prominent photospheric absorption features \ion{K}{i}~$\lambda\lambda$7664.911,~7698.974.
This gives us $\mathrm{RV_{LHS49}=}-22.6\pm0.5\,\kmps$, which is
in good agreement with the earlier measurement of \citet{garcia-sanchez:2001}
who found $\mathrm{RV_{LHS49}=}-21.7\pm1.8\,\kmps$. The heliocentric
RV of each object can be then calculated by adding $\mathrm{RV_{LHS49}}$
with the RV of each object with respect to LHS~49. In the following
measurements of the heliocentric radial velocities, our measurement
($\mathrm{RV_{LHS49}=}-22.6\pm0.5\,\kmps$) will be used for consistency.

@@

The result of the heliocentric RV measurements (from two epochs for
each object) is summarised in Table~\ref{tab:summary_results} along
with the uncertainties. The table also lists the uncertainties in
the `relative' radial velocities ($\sigma_{\mathrm{RRV}}$) which
is the uncertainty of RV with respect to the template star. The
two consecutive measurements of RVs (from same nights) are used to
find the RV of the night, and their uncertainties are obtained from
the standard deviations of the mean ($\sigma_{\mathrm{RRV}}$) and
the uncertainty of the template RV value (c.f.~\citealt{joergens:2006}).
(XXX What do you need to include the uncertainty in the template
star measurement when we are looking for relative changes in the
bd RVs?) The 'average' radial velocities ($\overline{\mathrm{RV}}$) of the
two epochs are also given in the same table. The $\overline{\mathrm{RV}}$
values of the objects in UScoOB are consistent with the earlier measurements
of \citet{muzerolle:2003} in Table~\ref{tab:literatures}, except
for the values for USco~66 and USco~75. This is unsurprising
since the former is a known binary \citep{kraus:2005} and the latter
is a non-constant RV object (a candidate for a multiple) found in
the RV-shift test which will be discussed next.

For each object and for each RV measurement, the deviations ($\Delta\mathrm{RV}$)
from the average RV are computed and summaries in Fig.~\ref{fig:radvel01}
along with their uncertainties ($\sigma_{\mathrm{RRV}}$) in order
to aid the identification of multiplicity candidates. Note that in
computing $\Delta\mathrm{RV}$ we do not require the knowledge of
absolute or the heliocentric radial velocities, but only the relative
velocities (with respect to a template). We identify an object as a candidate
when the 1$\sigma_{\mathrm{RRV}}$ error bar from each RV measurement
overlaps one another. Using this simple criteria, the candidate were
selected and indicated in the same table (Table~\ref{tab:summary_results}).
We found 9 out of 18 (50 per cent of) our sample are considered as
candidates. The recent observation of \citet{kraus:2005} (which was
not known to authors at the time of our observation: April--May, 2004)
confirms that USco~65 and USco~66 are multiple systems, and USco~109
is most likely a multiple system. In our RV-shift tests, we found
all the multiples confirmed by \citet{kraus:2005} in our multiple
candidates. Further they found USco~67, 128, 130, 132 as non-multiple,
and similarly we found them as 'non-candidates' for multiplicity.
The discrepancy between their results and ours are only in USco~75
and USco~112. While our results suggests that these are candidates
for multiple systems, \citet{kraus:2005} did not find them as multiple
systems. This difference may be caused by the difference in sensitivity
(on a binary separation) of the two different methods. Another possible
caused of the difference is that the uncertainties in RVs may be underestimated, since
surface activity of the objects may also contribute noise in
the RV measuements; however, the levels of th noise is expeted be
small for BD and VLM stars (c.f.~\citealt{joergens:2006}).

@@

According to the hydrodynamical simulations of a low-mass star-forming
cluster of \cite{bate:2003} which yields a stellar density of $1.8\times10^{3}\,\mathrm{stars\, pc^{-3}}$,
the rms dispersion (1-D) of the stars and the BDs is $1.2\,\kmps$.
Similarly for the model with a higher stellar density ($2.6\times10^{3}\,\mathrm{stars\, pc^{-3}}$),
the rms dispersion is 2.5~$\kmps$ (\citealt{bate:2005}). The standard
deviation of $\overline{\mathrm{RV}}$ ($1.2\,\kmps$) found in our
analysis is more comparable the lower stellar density model.

@@

\caption{Histogram of the average heliocentric radial velocities (left) and the rotational velocities (right) of 14 UScoOB BD and VLM objects listed in Table~\ref{tab:summary_results} (excluding USco~121, a non-member). The gaussian fit (dashed line) of the radial velociity distribution gives a standard deviation of  $1.2\,\kmps$ and the peak position of $-5.9\,\kmps$.  The log-normal fit (dash-dot) of  the rotational velocity distribution gives  a standard deviation $27.8\,\kmps$ and the peak poistion $16.9\,\kmps$.}
\label{fig:vrad_vrot_histrogram}

@@

The rotational velocities of the objects were determined by measuring
the widths of the cross correlation functions of the target spectra against
a template spectrum from an object which is known to have a very small
rotational velocity. The line broadening of the targets is assumed
to be dominated by rotational broadening. As in the cases for the
radial velocity measurements, LHS~49 is chosen as the template.
Using its rotational period ($P\approx83\,\mathrm{d}$, \citealt{benedict:1998})
and radius ($R_{*}\approx0.145\,\mathrm{R_{\odot}}$ from the VLTI
measurement by \citealt{segransan:2003}), the rotational velocity
of LHS~49 is estimated as $v\,\sin i=2\pi R_{*}/P\approx0.1\,\kmps$;
negligibly small.
